\documentclass{scrartcl}

\usepackage{blindtext}
\usepackage{hyperref}

\hypersetup{
    colorlinks=true,
    linkcolor=blue,
    filecolor=magenta,
    urlcolor=cyan,
    pdftitle={Lancaster University Computer Science Society Directive 2023.03.001},
    pdfpagemode={UseOutlines},
    breaklinks=true,
}

\urlstyle{same}

\title{Lancaster University Computer Science Society Directive 2023.03.002}
\subtitle{The Standing of the Society on Matters Pertaining to Politics et al.}
\author{Jonathan Leeming}
\date{March 2023}


\begin{document}
    \maketitle
    
    \clearpage
    \tableofcontents

    \clearpage
    \section{Preface}
        \label{preface}
        \subsection{Format}
            \label{preface--format}
            All sections of this document are to be considered normative, unless otherwise specified.

    \clearpage
    \section{Political Standing}
        \label{political-standing}
        \begin{enumerate}
            \item In all matters political, or such as may be construed as political, the Society shall have no stance.
            \item In any other matter, reasonable discretion, unimpeded by the fires of passion, shall be applied to determine the suitability of societal opinion.
            \item In exception circumstances, a petition may be brought to the Upper Cabinet for an exemption to permit standing.
                \subitem Such an appeal shall be granted only by unanimity amongst the Upper Cabinet.
        \end{enumerate}

    \clearpage
    \section{Personal Standing}
        \label{personal-standing}
        \begin{enumerate}
            \item To the extent permitted by superior documentation, Membership of the Society shall not prevent individuals from holding any viewpoint.
            \item In the event that an expression of a Personal Standing may reasonably be conflated with the standing of the Society, an appropriate declaration to the contrary shall be produced by the relevant Members.
        \end{enumerate}

    \clearpage
    \section{Disciplinary Measures}
        \label{disciplinary-measures}
        \begin{enumerate}
            \item Violation of this directive by a Member of the Executive shall be grounds for Impeachment of said Member.
            \item Members in violation of this directive may, at the discretion of the Cabinet and in accordance with Bye-Law 2023.03.002, by subject to exclusion or expulsion from the Society or Societal Activities.
        \end{enumerate}
\end{document}
 
