\documentclass{scrartcl}

\usepackage{blindtext}
\usepackage{hyperref}

\hypersetup{
    colorlinks=true,
    linkcolor=blue,
    filecolor=magenta,
    urlcolor=cyan,
    pdftitle={Lancaster University Computer Science Society Bye-Law 2023.03.000},
    pdfpagemode={UseOutlines},
    breaklinks=true,
}

\urlstyle{same}

\title{Lancaster University Computer Science Society Bye-Law 2023.03.000}
\subtitle{Aims of the Society}
\author{Jonathan Leeming}
\date{March 2023}


\begin{document}
    \maketitle
    
    \clearpage
    \tableofcontents

    \clearpage
    \section{Preface}
        \label{preface}
        \subsection{Format}
            \label{preface--format}
            All sections of this document are to be considered normative, unless otherwise specified.

        \subsection{Purpose}
            \label{preface--purpose}
            This section is non-normative.

            The purpose of this document is to describe the aims and intentions of the society.

    \clearpage
    \section{Aims}
        \label{aims}
        \begin{enumerate}
            \item The society aims to promote an interest both in members and in the wider community and public of computing, computer science, and information technology.
            \item The society aims to support members in their academic study of computing, computer science, and information technology.
            \item The society aims to provide networking opportunities for members with potential colleagues and employers.
            \item The society aims to provide a forum to facilitate between members discussion and debate on issues and topics concerning computing, computer science, and information technology.
        \end{enumerate}

    \clearpage
    \section{Events}
        \label{events}
        \subsection{Educational Events}
            \label{events--educational}
            \begin{enumerate}
                \item An Educational Event is an event which has been organised explicitly for educational purpose.
                \item At regular intervals through the year should be organised workshops and seminars for the purpose of revision of course material.
                \item At regular intervals through the year should co-curricular lectures should be arranged to be given by members of SCC and related faculties from partner universities.
                \item Consumption of alcohol is prohibited at Educational Events.
            \end{enumerate}

        \subsection{Social Events}
            \label{events--social}
            \begin{enumerate}
                \item A Social Event is an event which has been organised explicitly for the informal convention of members.
                \item Following shortly from Welcome Week should be at least one Social Event for the induction of new members.
                \item Prior to the commencement of each term should be publicised a calendar of the headline Social Events of the term.
                \item Additional Social Events should be held around major events.
                    \subitem For events organised in consultation with external parties, said parties should be provided opportunity for consultation of additional Social Events.
                \item Consumption of alcohol at Social Events is restricted only by the requirements of Union documentation.
            \end{enumerate}
\end{document}
 
